---
title: "Mini Assignment 5"
author: "Aakanksha Baid"
date: "2/17/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Step 1: Load the training

```{r}
ctrtrain <- read.csv("tgTrain.csv")
str(ctrtrain)
```

## Step 2: Subset data

```{r}
app1 <- ctrtrain[which(ctrtrain$app == 1),]
app2 <- ctrtrain[which(ctrtrain$app == 2),]
```



## Step 3: Find the mean CTR for the two apps.

```{r}
summary(app1)
summary(app2)
```

From above, the mean CTR for app 1 or mean clicks observed is 0.01216 or 1.22%. 
The mean CTR for app 2 or mean clicks observed is 0.0006029 or 0.06%. The mean CTR of the two apps are different with app 1 CTR higher than that of app 2.


## Step 4: Run a t.test and draw inferences

```{r}
t.test(app1$click,app2$click)
```

Based on the results, as p-value < 0.05, there is a statistically significant difference between the CTR of app 1 and app 2. So we reject the null hypothesis that the two mean clicks from app 1 and app2 are equal. 